Finance and Income Inequality - panel BMA approach\thanks{We thank two anonymous referees, ...}

### 2019-11-28 Paper/paper.tex
Updates from Overleaf
191128 update

%!TEX program = xelatex

@@

\setlength\parindent{34pt}
\onehalfspacing
\title{Finance and Wealth Inequality\thanks{We thank two anonymous referees, ...}}
\author[a]{Roman Horvath}
\author[a]{Jan Mares\footnote{\footnotesize Corresponding author's address: IES FSV UK, Opletalova 26, 110 00, Praha 1; \textbf{e-mail:janxmares@gmail.com}}}
\affil[a]{Charles University, Prague}

@@

\section{Related literature}
% \label{sec:literature}
\citet{pikettyandzucman2014}
\section{Data}
% \label{sec:data}

@@

\section{Concluding Remarks}
% \label{sec:conclusion}

>>>>

%!TEX program = xelatex
%!BIB program = bibtex

@@

\setlength\parindent{34pt}
\onehalfspacing
\title{Finance and Income Inequality - panel BMA approach\thanks{We thank two anonymous referees, ...}}
\author[a]{Roman Horvath}
\author[a]{Jan Mares\footnote{\footnotesize Corresponding author's address: IES FSV UK, Opletalova 26, 110 00, Praha 1; \textbf{e-mail:janxmares@gmail.com}}}
\affil[a]{Charles University, Prague}

@@

\section{Related literature}
% \label{sec:literature}
\citet{pikettyandzucman2014}
\citet{van2018inequality} provide evidence that income inequality in the \ac{us} has different implications for the future income growth of the rich and the poor. High inequality seems to hurt the prospects of the poor while the top for the distribution is unaffected. The rich thus disproportianately benefit from higher inequality as their subsequent income exhibit faster growth. The authors attribute this effect to the political channel the rich use to lobby for implementation for the policies which back their economic interests. Preferences of the rich  are ultimately more likely to determine public policy than the preferences of the majority \citep{gilens_page_2014}. High inequality together with a credit constraint and rich driving the political process results in low government spending and lasting high inequality.

\citet{marrero2013inequality} introduce two types of inequality - inequality of oppportunity and inequality of effort/luck. Applying this to the EU countries and US states, they show that inequality of opportunity (driven by race, parental education, citizenship, ...) is negatively related to growth while the residual "good" inequality is growth inducing.

\section{Data}
% \label{sec:data}

@@

% \label{sec:conclusion}
